### 2024-05-05 paper/sec/3_methods.tex
Add files via upload
Update 3_methods.tex

\subsection{Feature Transform}
\indent For a given video, OpenPose outputs a directory of json files, with one for each frame. Before passing these outputs to a 
second machine learning model, we wanted an algorithm that could map similar poses and movements to the same values, 
regardless of camera angle or relative location of the person to the camera. (Due to the nature of OpenPose outputting x, 
y values for keypoints, we have already circumvented the issue of changes in illumination.)  Our keypoint-to-angle algorithm 
aims to:
\begin{itemize}
    \item Greatly reduce the role of absolute pixel locations in identifying features
    \item Make the model invariant to differences in the user’s body structure
    \item Detect straight-line, elliptical, and hybrid motion
\end{itemize}

>>>>

\includegraphics[width=\columnwidth]{sec/openpose_demo}
\textit{Figure 1. OpenPose in action: pose detection on a frame from an input video of two people. 
OpenPose accurately detects the key points on both people despite their slightly unorthodox body positions.}

\subsection{Feature Transform}
\indent For a given video, OpenPose outputs a directory of JSON files, with one for each frame. Before passing these outputs to a 
second machine learning model, we wanted an algorithm that could map similar poses and movements to the same values, 
regardless of camera angle or relative location of the person to the camera. (Due to the nature of OpenPose outputting x, 
y values for keypoints, we have already circumvented the issue of changes in illumination.)  Our keypoint-to-angle algorithm 
aims to:
\begin{itemize}
    \item Greatly reduce the role of absolute pixel locations in identifying features
    \item Make the model invariant to differences in the user’s body structure
    \item Detect straight-line, elliptical, and hybrid motion
\end{itemize}
